Hypertension and microbiome

### 2019-06-14 articletwo.Rmd
Correct image size for maaslin plot
Variable missing

ggsave(file = "cache/maaslin.png", plot = maaslinplot, height = 30, width = 40, unit = "in", dpi = 300)
```

@@

```{r salt characteristics}
pseq.genus.salt %>%
    meta %>%
    gather(key,value) %>%
    group_by(key) %>%
    summarise_all(funs(N = n(),
                       Mean = mean(as.numeric(value), na.rm = TRUE),
                       sd = sd(as.numeric(value), na.rm = TRUE),
                       NAs = sum(is.na(value))))  %>%
    mutate_if(is.numeric, round, 3) %>%
    kable()
```

>>>>

ggsave(file = "cache/maaslin.png", plot = maaslinplot, height = 3, width = 4, unit = "in", dpi = 300)
```

@@

```{r salt characteristics}
df.genus.salt %>%
    select(-Sample) %>% 
    gather(key,value) %>%
    group_by(key) %>%
    summarise_all(funs(N = n(),
                       Mean = mean(as.numeric(value), na.rm = TRUE),
                       sd = sd(as.numeric(value), na.rm = TRUE),
                       NAs = sum(is.na(value))))  %>%
    mutate_if(is.numeric, round, 3) %>%
    kable()
```
